Comparing MTurk and the US Population's Occupational Diversity

### 2018-11-05 Manuscript.Rmd

#- - - - - - - - - - - - - 
#insert table 2 about here
#- - - - - - - - - - - - -

>>>>

#- - - - - - - - - - - - - 
#insert table 2 about here
#- - - - - - - - - - - - - 
##Chart 1
```{r}
#Bar Plot with error bars
require(ggplot2)
Values <- c(Table2[1:13, 5], Table2[1:13, 2])
Group <- c("MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "MTurk", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS", "BLS")
Occupations <- c(Table2[1:13, 1], Table2[1:13, 1])
Occ_Nums <- sapply(strsplit(Occupations, " "), "[[", 1)
barplot_data <- data.frame(as.character(Values), as.character(Occ_Nums),as.character(Group))
names(barplot_data) <- c("Frequency", "Occupations","Group")
dodge <- position_dodge(width = .9)

#Define Error Bar limits.
upperM <- as.vector(Table2[1:13, 6])
upperB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
upper <-c(upperM, upperB)

lowerM <- as.vector(Table2[1:13, 6])
lowerB <- c(0, 0,0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0)
lower <- c(lowerM, lowerB)

se <- data.frame(upper, lower)
limits <- aes(ymax = se$upper, ymin = se$lower)

require(ggplot2)
ggplot(barplot_data, aes(Occ_Nums, Values, fill = Group)) + 
  geom_errorbar(limits, position = dodge,
                width = 0.10, size = 1.0) +
  geom_col(position = dodge)  +
  ggtitle("MTurk's Occupational Diveristy with Error Bars") +
  labs(x = "Occupation", y = "Frequency") +
  theme(legend.position = "top", plot.title = element_text(hjust = 0.5), 
        text=element_text(family="serif"))+
  coord_flip()
```
